# Open Peer Review 

This exercise is about identifying reproducibility issues in a scientific publication. We use the criteria for reproducibility that are publicly available.
<br> <br>
```{r read criteria table, echo=FALSE}
#load table containing criteria
knitr::kable(read_excel("data/data_raw/002_open_peer_review/reproducibility_criteria.xlsx"), 
             align = 'c', 
             caption = "Reproducibility criteria"
             )
```
__Table clarification__ The Transparency Criteria are criteria needed to score an article of your choice. Each Transparency criterion comes with a Definition that explains the criterion in more details. These descriptions are particularly helpful to understand what the criterion entails and what to look for in the article. The Response Type is the actual score.  [Source](https://www.researchgate.net/publication/340244621_Reproducibility_and_reporting_practices_in_COVID-19_preprint_manuscripts/fulltext/5e81f9fd92851caef4ae37ba/Reproducibility-and-reporting-practices-in-COVID-19-preprint-manuscripts.pdf)
<br> <br>
I found an open access scientific article using [PubMed](https://pubmed.ncbi.nlm.nih.gov/) and scored it using the table above.
<br> 
Article: <br>
[Yamayoshi S, Sakai-Tagawa Y, Koga M, et al. Comparison of Rapid Antigen Tests for COVID-19. Viruses. 2020;12(12):1420. Published 2020 Dec 10. doi:10.3390/v12121420](https://pubmed.ncbi.nlm.nih.gov/33322035/)
<br> <br>
Study purpose   -   Present <br>
Data availability statement   -   Not present <br>
Data location   -   Present <br>
Study location    -   Present <br>
Author review   -   Not present <br>
Ethics statement    -   Present <br>
Funding statement   -   Present <br>
Code availability   -   Not present
<br> <br>
In the study rapid antigen tests (RAT) for covid-19 are tested on corona positive patients to compare their effectivity to the PCR method. To do this, patient material such as saliva and nose/throat swabs were used with four types of RATs and the standard PCR test. The RATs were also tested using 2 isolated virus strands. The RATs were less sensitive than the PCR test. Some of the RATs are not able to detect low quantities of virusparticles. There is no big difference between the isolated virus and the clinical samples. 
Data is available onine [here](https://www.mdpi.com/1999-4915/12/12/1420/s1).
<br> <br>
Next I used the [OSF website](https://osf.io/) to select a project that adresses an aspect of the SARS-Cov-2 virus and contained a dataset and R-code in the project enviorment. <br>
I found the project [Bats and COVID-19](https://osf.io/wxh6a/)
<br> <br> 
The code in this project intends to compare the search words 'coronavirus' and 'bats' through Google and wikipedia in multiple countries and score how often they were used together. <br>
The readability of the code is a 4/5. 
<br>
Click [here](data/data_raw/002_open_peer_review/bats_and_covid.R) to see the full code from the article.
<br> <br> 
Now lets reproduce some of the code: 
<br>
``` {r bats_and_covid.R code, message = FALSE, warning = FALSE}
### Display code chunk from bats_and_covid.R file.###
# Fig.1 (2016-2020 US Tv news about bats) 
{
  tv.dat <- 
      read.csv(file="data/data_raw/002_open_peer_review/GDELTBatsUS1620.csv")
  tv.dat$date <- ymd(tv.dat$date)
  tv.dat[61, "date"] <- "2021-01-01"
  tv.dat[61, "value"] <- NA
  tv.dat[61, "X"] <- 61
  ggplot() + 
    geom_line(data=tv.dat, aes(x=X, y=value), size=0.8, color="steelblue", linetype="solid") + 
    theme_bw() + 
    scale_x_continuous(breaks=c(1, 13, 25, 37, 49, 61), labels=c("2016", "2017", "2018", "2019", "2020", "2021")) +
    theme(axis.text.x = element_text(colour="black",size=14,angle=0,hjust=.5,vjust=.5,face="plain"),
          axis.text.y = element_text(colour="black",size=14,angle=0,hjust=1,vjust=0,face="plain"),  
          axis.title.x = element_text(colour="black",size=12,angle=0,hjust=.5,vjust=.5,face="plain"),
          axis.title.y = element_text(colour="black",size=12,angle=90,hjust=.5,vjust=.5,face="plain"),
          plot.title = element_text(size=22, face="bold")) +
    theme(strip.background =element_rect(fill="wheat")) + labs(x="", y="") +
    theme(strip.text = element_text(colour = "black", size=14, face="bold"))
}
``` 
<br>
Reproducibility errors: I adjusted data location and loaded library lubridate.
<br>
It took very low effort (4/5) to reproduce the code. 
<br>
Lack of pseudo coding makes the data somewhat more difficult to interpret. 
