Portfolio assignment 1.2{.unnumbered}
================================================================================
Assignment {.unnumbered}
--------------------------------------------------------------------------------
Open Peer Review

This exercise is about identifying reproducibility issues in a scientific publication. We use the criteria for reproduciblity that are publically available via here

```{r read criteria table, echo=FALSE}
knitr::kable(read_excel("data/data_raw/reproducibility_criteria.xlsx"), 
             align = 'c', 
             caption = "Reproducibility criteria"
             )
```
__Table clarification__ The Transparency Criteria are criteria you need to score the article of your choice for. Read them carefully and discuss with another course participant if you do not understand them. Each Tranparance criterion comes with a Definition that explains the criterion in more details. These descriptions are particularly helpful to understand what the criterium entails and what to look for in the article. The Response Type is the actual score

In this assisgment you need to find a scientific article yourself, using PubMed or another database or repository. Use only Open Access articles. Having an article in hand, go over the table above and score the article according the criteria. Be sure to select a primary article that presents a study using data from experimental work . This can be laboratory experiments or in silico experiments. Reviews and meta analysis are not suitable for this assignment

To guide your search you can choose between these topics

“Coronavirus / COVID-19”<br>
“The effects of compound on an organism / Toxicology”<br>
“The effectiveness of a drug or treatment in an animal study”<br>
“The effects of a compound investigated in a cell or organoid system”

TIPS<br>
If you do not know where to start your literature search start here: https://www.biorxiv.org/ <br>
This assignment is not about the topic you select, so try to do that quickly <br>
You may want to cheat and select an article that scores TRUE on the Data Availability Statement, because that enables you to use the this article again in one of the next assignments. 

PART 1 To complete part 1, execute activity A to G

__A.__ Initiate an empty RMarkdown file in your RStudio environment and provide author and title (after the title of this exercise)

__B.__ Search for a primary Open Access article on one of the above listed topics, using Pubmed Central

__C.__ Read the article diagonally to check if is indeed a primary article describing emperical scientific findings.

__D.__ Include the reference to this article in your Rmd file

__E.__ Score the article on the basis of the above ‘Repita’ criteria

__F.__ Write an Rmarkdown report on your findings, including the table above and some information about the article such as general aim, short methods and results. If data is available, try including some

__G.__ Store the source Rmd and knitted HTML in a folder called ‘Rmd’ in your course RStudio project. You will need it again later in the course

PART 2 To complete this assignment you will have to execute activity H to P

__H.__ Using the OSF website, select a project that addresses an aspect of the SARS-Cov-2 virus.

__I.__ Select a project that has a dataset and R-code shared in the project environment.

__J.__ Have a look at the code. Describe in your own words what the code intents to achieve.

__K.__ In terms of readibility of the code, how would you grade (1(very bad)-5(very good)) the code available.

__L.__ Download the code and the data to a new RStudio project

__M.__ Run the script or code that is available to reproduce at least 1 figure

__N.__ When you encounter errors or flaws in the script, try fixing them and record your changes.

__O.__ Taken together on a scale from 1 (very hard) to 5 (very easy), how much effort did it take you to reproduce the visualization from the project, report or article

__P.__ Generate an RMarkdown script that contains the details on the project you selected, the code you used to create the visualization and your score for reproducibility.

resource: https://www.researchgate.net/publication/340244621_Reproducibility_and_reporting_practices_in_COVID-19_preprint_manuscripts/fulltext/5e81f9fd92851caef4ae37ba/Reproducibility-and-reporting-practices-in-COVID-19-preprint-manuscripts.pdf

Part 1, A-G {.unnumbered}
--------------------------------------------------------------------------------
Article: <br>
Yamayoshi S, Sakai-Tagawa Y, Koga M, et al. Comparison of Rapid Antigen Tests for COVID-19. Viruses. 2020;12(12):1420. Published 2020 Dec 10. doi:10.3390/v12121420

Study purpose   -   Present <br>
Data availability statement   -   Not present <br>
Data location   -   Present <br>
Study location    -   Present <br>
Author review   -   Not present <br>
Ethics statement    -   Present <br>
Funding statement   -   Present <br>
Code availability   -   Not present

In the study rapid antigen tests (RAT) for covid-19 are tested on corona positive patients to compare their effectivity to the PCR method. To do this patient material such as saliva and nose/throat swabs were used with four types of RATs and the standard PCR test. The RATs were also tested using 2 isolated virus strands. The RATs were less sensitive than the PCR test. Some of the RATs are not able to detect low quantities of virusparticles. There is no big difference between the isolated virus and the clinical samples. 
Data is available onine at: https://www.mdpi.com/1999-4915/12/12/1420/s1

Part 2, H-P {.unnumbered}
--------------------------------------------------------------------------------
project: <br>
Bats and COVID-19 - https://osf.io/wxh6a/

The code intends to compare the searchwords 'coronavirus' and 'bats' through google and wikipedia in multiple countries.

Readability is a 4/5.

See bats_and_covid.R for the code and to run it.

Code:
``` {r bats_and_covid.R code, eval=FALSE}
######################
###Fig.1 (2016-2020 US Tv news about bats) {.unnumbered}
{
  tv.dat <- 
    read.csv(file="GDELTBatsUS1620.csv")
  tv.dat$date <- ymd(tv.dat$date)
  tv.dat[61, "date"] <- "2021-01-01"
  tv.dat[61, "value"] <- NA
  tv.dat[61, "X"] <- 61
  ggplot() + 
    geom_line(data=tv.dat, aes(x=X, y=value), size=0.8, color="steelblue", linetype="solid") + 
    theme_bw() + 
    scale_x_continuous(breaks=c(1, 13, 25, 37, 49, 61), labels=c("2016", "2017", "2018", "2019", "2020", "2021")) +
    theme(axis.text.x = element_text(colour="black",size=14,angle=0,hjust=.5,vjust=.5,face="plain"),
          axis.text.y = element_text(colour="black",size=14,angle=0,hjust=1,vjust=0,face="plain"),  
          axis.title.x = element_text(colour="black",size=12,angle=0,hjust=.5,vjust=.5,face="plain"),
          axis.title.y = element_text(colour="black",size=12,angle=90,hjust=.5,vjust=.5,face="plain"),
          plot.title = element_text(size=22, face="bold")) +
    theme(strip.background =element_rect(fill="wheat")) + labs(x="", y="") +
    theme(strip.text = element_text(colour = "black", size=14, face="bold"))
}
##################################
``` 

Errors: Adjusted data location and loaded library lubridate.

It took very low effort (4/5) to reproduce the code.
