---
params: 
  data: https://opendata.ecdc.europa.eu/covid19/nationalcasedeath_eueea_daily_ei/csv
---

# Parameterized data 

For this page the [COVID-19 case data](https://www.ecdc.europa.eu/en/publications-data/data-daily-new-cases-covid-19-eueea-country) from the European Center for Disease Control (ECDC) was used to create a parameterized report of COVID-19 cases and deaths in the Netherlands from the first data in February 2020 to end of March 2022. February 2nd 2022 was excluded from this range because this date had an abnormally high value. This is probably because of Dutch labs not being able to process the high number of covid-PCR tests taken around this date.<br> <br>
Information about the data can be found [here](https://www.ecdc.europa.eu/sites/default/files/documents/Description-and-disclaimer_daily_reporting.pdf)
<br>
```{r calling and adjusting data,  results = "hide", message = FALSE, warning = FALSE}
# Filter the data. The first and last line change the date format so the first column can be specified as such
lct <- Sys.getlocale("LC_TIME"); Sys.setlocale("LC_TIME", "C")

utils::data(list = params$data)
covid_data <- readr::read_csv(params$data)
covid_data_filtered <- covid_data %>% 
  dplyr::filter(countriesAndTerritories %in% "Netherlands") %>% 
  transform(dateRep = as_date(dateRep, format = "%d/%m/%Y")
            )

covid_data_filtered <- covid_data_filtered[-c(43),]

Sys.setlocale("LC_TIME", lct)
```
```{r creating graphs, message = FALSE, warning = FALSE}
# Make ggplot containing covid cases and deaths in the Netherlands during period Jan 2021 to May 2021
cases <- covid_data_filtered %>% ggplot2::ggplot(aes(x = dateRep, y = cases)) +
  geom_line(colour = "blue", size = 2) +
  theme(legend.position = "none") +
    labs(title = "COVID-19 cases in the Netherlands", 
       subtitle = "Recorded COVID-19 cases in the Netherlands by date",
       x = "Month",
       y = "Cases"
       )

deaths <- covid_data_filtered %>% ggplot2::ggplot(aes(x = dateRep, y = deaths)) +
  geom_line(colour = "red", size = 2) +
  theme(legend.position = "none") +
    labs(title = "COVID-19 deaths in the Netherlands", 
       subtitle = "Recorded COVID-19 deaths in the Netherlands by date",
       x = "Month",
       y = "Deaths"
       )
# Plot for cases
cases
# Plot for deaths
deaths
```
<br>
What stands out in the graphs is that even though the amount of Covid-19 cases starts rising more towards the end of the graph the amount of deaths decline. This could be due to the fact that the Delta- and Omicron variants of the Corona virus were less lethal even though they caused infections to spread more rapidly among the Dutch population. This becomes more evident when looking at the data from 2022. At the end of 2021 and the start of 2022, the Omicron variant started causing a rapid increase in the infection rate of Covid-19 but the amount of deaths in this time is incredibly low. Especially when compared to the number of cases. 
